\cvsection{CERTIFICATIONS}

\cvmetaevent
{Certified Kubernetes Security Specialist}
{}
{}
{Earners of this designation are accomplished Kubernetes practitioners.

Hands-on exam demonstrated the requisite abilities to secure container-based applications and Kubernetes platforms during build, deployment and runtime, and are qualified to perform these tasks in a professional setting.}

\cvmetaevent
{Certified Kubernetes Administrator}
{}
{}
{Holders of this designation demonstrated the skills, knowledge and competencies to perform the responsibilities of a Kubernetes Administrator.

That means demonstrating in hands-on scenarious in Application Lifecycle Management, Installation, Configuration and Validation

Core Concepts, Networking, Scheduling, Security, Cluster Maintenance, Logging Monitoring, Storage, and Troubleshooting.}

\newpage
\cvmetaevent
{Certified Kubernetes Application Developer}
{}
{}
{Earners of this designation demonstrated the skills, knowledge and competencies to perform the responsibilities of a Kubernetes Application Developer. Earners are able to define application resources and use core primitives to build, monitor, and troubleshoot scalable applications and tools in Kubernetes. The skills and knowledge demonstrated by earners include Core Concepts, Configuration, Multi-Container Pods, Observability, Pod Design, Services and Networking, State Persistence.}

\cvmetaevent
{Kubernetes and Cloud Native Associate}
{}
{}
{Basic knowledge of Kubernetes and cloud-native technologies, including how to deploy an application using basic kubectl commands, the architecture of Kubernetes , understanding the cloud-native landscape and projects (storage, networking, GitOps, service mesh), and understanding the principles of cloud-native security was acknowledged by successful passing.}

\cvmetaevent
{Kubernetes and Cloud Native Security Associate}
{}
{}
{Participans holding this badge have demonstrated an understanding of the baseline security configuration of Kubernetes clusters to meet compliance objectives, including the ability to harden security controls, test and monitor the security, and participate in assessing security threats and vulnerabilities.}

\newpage
\cvmetaevent
{PCA: Prometheus Certified Associate}
{}
{}
{Earners of this designation demonstrated an understanding of best practices for monitoring cloud native applications and infrastructure using Prometheus, including how to use observability data to improve application performance, troubleshoot system implementations, and feed that data into other systems.}

\cvmetaevent
{ICA: Istio Certified Associate}
{}
{}
{Earners of this designation demonstrated a solid understanding of Istio principles, terminology, and best practices in order to set up Istio.}

\cvmetaevent
{CAPA: Certified Argo Project Associate}
{}
{}
{Earners of this designation demonstrated a solid understanding of the Argo Project ecosystem, terminology, and best practices for each tool and how it relates to common DevOps, GitOps, Platform Engineering, and related practices.}

\cvmetaevent
{CGOA: Certified GitOps Associate}
{}
{}
{Earners of this designation demonstrated comprehension of GitOps patterns including when and why to use them. They also understand the precautions to take around tooling for manifest format and packaging, state store systems, and reconciliation engines to adhere to and extend GitOps principles.}

