\cvsection{EDUCATION}

\cvmetaevent
{Since 2024}
{Udemy Instructor}
{Tekton - The quick start}
{As an instructor for Tekton CI/CD, I am passionate about sharing my self-educated expertise gained from enterprise projects. My goal is to empower the community by disseminating knowledge on technologies and assisting individuals in their learning journey.}

\cvmetaevent
{2016 - 2020}
{B. Sc. - IT-Security}
{University of Darmstadt}
{I pursued a dual study program, earning a Bachelor of Science in IT Security. This program combined academic studies with practical work experience at an IT consulting company. During my studies, I gained in-depth knowledge of IT security principles, software engineering, and automation techniques. Concurrently, I applied this knowledge in real-world scenarios by working in blocks and during holidays at the consulting company, practicing what I had learned with actual customers.}

\cvmetaevent
{2014 - 2016}
{State certified technician}
{Technical College Braunschweig}
{I completed a two-year full-time education program as a State-Certified Technician in Computer Science. During this program, I gained advanced skills in programming, focusing on technical systems such as controllers and bus systems. I practiced software design methods and applied them in various projects, including a team-based project conducted outside the school setting. My studies also included operating systems and virtualization environments.}

\newpage
\cvmetaevent
{2010 - 2013}
{IT specialist - system integration}
{Company GEKA mbh}
{As an entry into the IT career, I completed an apprenticeship as an IT Specialist in System Integration. During this time, I worked as a system administrator for Windows domains and was responsible for electronic installations in the data center. My role involved managing both hardware and software components, with a significant focus on automation processes.}
